``Interestingness'' in Mathematical Theory Exploration

### 2019-10-18 PhDThesis/litreview.tex
Thesis changes (e.g. lit review)
More content
Bunch more changes to thesis
Disable some bits of litreview for now
Headingy things
TODOs
Add intro

\section{Literature Review}

\input{litreview_mathhistory.tex}
\input{litreview_interestingness.tex}
\input{litreview_theoryformation.tex}
\input{litreview_theoryexploration.tex}
\input{litreview_premiseselection.tex}

>>>>

\chapter{Literature Review}

In this chapter we place existing work on Theory Exploration in context, survey
related fields and those which we draw our own contributions and inspirations
from; including Machine Learning, tools for identifying and applying
improvements to software, premise selection in (automated and interactive)
theorem proving, and measures for determining the ``interestingness'' of a
statement or conjecture.

\input{litreview_automatedreasoning.tex}
\input{litreview_staticanalysis.tex}
\input{litreview_testing.tex}
\input{litreview_premiseselection.tex}
\input{litreview_machinelearning.tex}
\input{litreview_interestingness.tex}
